Appendix: Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2025-05-15 appendix.qmd
Updated Figure 3

triangle_plot <- ggplot() +
  # geom_point(
  #   data = triangle_temp,
  #   aes(
  #     x = x,
  #     y = y
  #   )
  # ) +
  geom_segment(
    data = triangle_line_temp,
    aes(
      x = x,
      xend = xend,
      y = y,
      yend = yend
    )
  ) + 
  annotate("text", x=-1, y= 1.5, 
           label = expression(frac(a[2] - a[1], 2)), 
           color = "black", hjust=-0.2, size = 5) + 
  annotate("text", x=1.5, y= -0.3, 
           label = expression(frac(a[1], 2)), 
           color = "black", hjust=-0.2, size = 5) + 
  annotate("text", x=2.5, y= 1.5, 
           label = expression(l), 
           color = "black", hjust=-0.2, size = 5)
```

>>>>

triangle_plot <- ggplot() +
  # geom_point(
  #   data = triangle_temp,
  #   aes(
  #     x = x,
  #     y = y
  #   )
  # ) +
  geom_segment(
    data = triangle_line_temp,
    aes(
      x = x,
      xend = xend,
      y = y,
      yend = yend
    )
  ) + 
  annotate("text", x=-1.5, y= 1.5, 
           label = expression(frac(a[2] - a[1], 2)), 
           color = "black", hjust=-0.2, size = 8) + 
  annotate("text", x=1.5, y= -0.5, 
           label = expression(frac(a[1], 2)), 
           color = "black", hjust=-0.2, size = 8) + 
  annotate("text", x=2.5, y= 1.5, 
           label = expression(l), 
           color = "black", hjust=-0.2, size = 8)
```
